A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-25 text/manuscript.Rmd
added url for the CDC data

We used Bayesian inference to explore the relative impact of cancer diagnosis on
survival at the time of diagnosis. Our model assumes that at birth each person
has a small initial probability per unit time to die, and that this probability
grows exponentially in time at some baseline rate that matches the observed CDC
data. The rate of growth in risk is assumed to jump to a higher level at
diagnosis, which we take as a proxy for onset. This represents an accelerated
aging type model. To fit the model, we constrain the baseline risks using the
available CDC life tables. We then constrain the cancer specific multiplier
using the longevity data within the cancer tumor dataset. Our model estimates
the effect of cancer type and class-specific cancer effects independently,
resulting in a cancer and class specific estimate of the aging rate multiplier.
A detailed description of the CDC longevity model and likelihood is provided in
the **Supplementary methods**.

>>>>

We used Bayesian inference to explore the relative impact of cancer
diagnosis on survival at the time of diagnosis. Our model assumes that
at birth each person has a small initial probability per unit time to
die, and that this probability grows exponentially in time at some
baseline rate that matches the observed CDC data. The rate of growth
in risk is assumed to jump to a higher level at diagnosis, which we
take as a proxy for onset. This represents an accelerated aging type
model. To fit the model, we constrain the baseline risks using the
available CDC life tables
(ftp://ftp.cdc.gov/pub/Health_Statistics/NCHS/Publications/NVSR/68_07/). We
also constrain the cancer specific multiplier using the longevity data
within the cancer tumor dataset. Our model estimates the effect of
cancer type and class-specific cancer effects independently, resulting
in a cancer and class specific estimate of the aging rate multiplier.
A detailed description of the CDC longevity model and likelihood is
provided in the **Supplementary methods**.
